---
title: "Augment JULES ensemble design"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{write-jules-ensemble-design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The purpose of this vignette is to augment an ensemble of JULES with new ensemble members, with input parameter configurations where we think the model output will fall within a set of constraints. The code will write a new set of configuration files.

```{r}

library(DiceKriging)
library(julesR)
library(emtools)
library(imptools)
library(viztools)


```



```{r}
years = 1861:2014
ysec = 60*60*24*365
norm_vec = c(1e12, 1e12, 1e12/ysec , 1e12, 1e12, 1e9)
 
# Load up the data
# system.file find the specified file in package julesR
lhs_i = read.table(system.file('extdata/lhs_u-ao732.txt', package = 'julesR'), header = TRUE)
lhs_ii = read.table(system.file('extdata/lhs_u-ao732a.txt', package = 'julesR'), header = TRUE)
 
toplevel_ix = 1:499
 
lhs = rbind(lhs_i, lhs_ii)[toplevel_ix, ]
 
X = normalize(lhs)
colnames(X) = colnames(lhs)
d = ncol(X)


#dat <- read.csv(system.file('extdata/es_ppe_ii_annual_global_sum.csv', package = 'julesR'), header = TRUE)
dat <- read.csv(file = '~/myRpackages/julesR/inst/extdata/es_ppe_ii_annual_global_sum.csv', header = TRUE)

Y <- sweep(dat, 2, norm_vec, FUN = '/')
p <- ncol(Y)

```

## Level 0 constraint

The model is required to run, and have some sort of functioning carbon cycle.

```{r, level 0 constraint}

allix = 1:(nrow(Y)) # this could be replaced with toplevel_ix above

# Constrain with global runoff and nbp, so that the emulator
# is not negatively affected by really bad points
level0_ix = which(Y[,'runoff'] >0.5 & Y[,'nbp'] > -10)
# 
Y_level0  = Y[level0_ix, ]     # (scaled to sensible) data that passes level 0
X_level0 = X[level0_ix, ]               # Normalised inputs that pass level 0
lhs_level0 = lhs[level0_ix, ]           # Non-normalised inputs that pass level 0
# 
nlevel0_ix = setdiff(allix, level0_ix)  # These inputs DO NOT PASS
X_nlevel0 = X[nlevel0_ix, ]
lhs_nlevel0 = lhs[nlevel0_ix, ]
#  
# These are the ensemble members which do not run (produce NA)
na_ix = which(is.na(Y[,'runoff']))
X_na = X[na_ix, ]
lhs_na = lhs[na_ix, ]

dim(Y_level0)
```


## Level 1 constraint

The model has a carbon cycle which is constrained to within broad ranges of a number of important outputs.

```{r}

# Apply level 1 constraints
level1_ix = which(Y[,'cs_gb'] > 750 & Y[,'cs_gb'] < 3000 &
  Y[,'cv'] > 300 & Y[,'cv'] < 800 & 
  Y[,'npp_n_gb'] > 35 &
  Y[,'npp_n_gb'] < 80 &
  Y[,'runoff'] >0.5 &
  Y[,'nbp'] > -10
  )

X_level1 = X[level1_ix, ]

# Ranges of the inputs after a level 1 constraint
rn_l1 = apply(X_level1, 2, range)

nlevel1_ix = setdiff(allix, level1_ix)
X_nlevel1 = X[nlevel1_ix, ]

Y_level1 = Y[level1_ix, ]

dim(Y_level1)
```


## Setup history matching limits

```{r}
# In order to use the history matching code, we'll need to specify targets -
# specifically "observations" with uncertainty thatapproximately match our
# "hard boundaries" from the existing constraints.

# Initial guess just choose the centre of the (implied) uniform distribution.
#cs_gb.target = (3000 - 750) / 2
#cv.target = (800 - 300) / 2
#npp_n_gb.target = (80 - 35) / 2
#runoff.target = 1
#nbp.target = 0
#gpp.target = 75

#Y.target = c(cs_gb.target, cv.target, npp_n_gb.target, runoff.target, nbp.target)

# I'm going to set it so that +3sd aligns approximately with the original limits
# given by Andy Wiltshire.
#cs_gb       cv    gpp_gb        nbp npp_n_gb    runoff
Y_lower = c(750, 300, 50, -10, 35, 0.5)
Y_upper = c(3000, 800,200, 10, 80, 1.5)
Y_target = (Y_upper - abs(Y_lower)) / 2 # abs() to fix the problem with negative numbers


# standard deviation is derived from the limits and the central target
# (this distance is assumed to be 3 standard deviations.
Y_sd = (Y_upper - Y_target) / 3
names(Y_sd) = colnames(Y)

obs_sd_list = as.list(rep(0.01,p))
disc_list =  as.list(rep(0,p)) 
disc_sd_list =  as.list(Y_sd/2)
thres = 3

mins_aug = apply(X_level1, 2, FUN = min)
maxes_aug =apply(X_level1, 2, FUN = max)

# convert Y_target for ingestion into function
Y_target = matrix(Y_target, nrow = 1)

```


```{r}
# Final output needs to be expressed in terms of original LHS, then put back out to conf files.

# This function adds n.aug potential design points, and finds their implausibility
# score in X.nroy

wave1 = addNroyDesignPoints(X = X_level1, 
                            Y = Y_level1, 
                            Y_target = Y_target,
                            n_aug = 10000, 
                            mins_aug = mins_aug,
                            maxes_aug = maxes_aug,
                            thres = 3,
                            disc_list=disc_list,
                            disc_sd_list = disc_sd_list,
                            obs_sd_list = obs_sd_list,
                            n_app = 20,
                            nreps = 100)
```



```{r}
source('default_jules_parameter_perturbations.R')

# Easiest way to generate a design of the right size is to have a "fac" which takes
# the names from the parameter list, and then multiplies everything by 0.5 or 2

tf <- 'l_vg_soil'
# we don't want anything that is TRUE/FALSE to be in fac
fac.init <- names(paramlist)
not_tf.ix <- which(names(paramlist)!=tf)
paramlist.trunc <-paramlist[not_tf.ix]

fac <- names(paramlist.trunc)

maxfac <-lapply(paramlist.trunc,function(x) x$max[which.max(x$max)] / x$standard[which.max(x$max)])
minfac <- lapply(paramlist.trunc,function(x) x$min[which.max(x$max)] / x$standard[which.max(x$max)])

```


```{r}
# create a directory for the configuration files
confdir <- 'conf_files_augment'

dir.create(confdir)

X_mm = wave1$X_mm

# This is the function that writes the configuration files.
write_jules_design(X_mm = X_mm, paramlist=paramlist, n = nrow(X_mm),
                    fac = fac, minfac = minfac, maxfac = maxfac,
                    tf = tf,
                    fnprefix = paste0(confdir,'/param-perturb-P'),
                    lhsfn = paste0(confdir,'/lhs_example.txt'),
                    stanfn = paste0(confdir,'/stanparms_example.txt'),
                    allstanfn = paste0(confdir,'/allstanparms_example.txt'),
                    rn = 12,
                    startnum = 100)
```

```{r}






```

```{r}
# Tighter restrictions on model outputs will lead to a smaller
# Xnroy object, as more potential inputs are ruled out.
dim(wave1$X_nroy)

# Exclude any design points outside of the ranges returned as NROY
keep1.ix = which(apply(X.level1, FUN = WithinRange,1,
                      maxes = wave1$X.nroy.max,
                      mins = wave1$X.nroy.min))

X.keep1 = X.level1[keep1.ix, ]

# choose the number of NROY design points that we require for the next wave
# of model runs.
n.app = 100

# The ChooseMaximinNroy algorithm picks a matrix which has space filling properties
X.aug1 = ChooseMaximinNroy(n.app = n.app, waveobj=wave1, nreps = 10000)


X2 = rbind(X.keep1, X.aug1)

# Express this matrix in terms of the original latin hypercube

# Visualise the various design matrices.
dev.new(width = 10, height = 10)
pairs(X.keep1, gap = 0, xlim = c(0,1), ylim = c(0,1)
)

# Here is the new part of the design.
# This has pleasing gaps with no design points, meaning we've ruled out parts of space.
dev.new(width = 10, height = 10)
pairs(X.aug1, gap = 0, xlim = c(0,1), ylim = c(0,1)
)


# end of analysis
stop()

```


Many of the ensemble members are removed under this constraint, with only around 10% remaining.




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
