---
title: "Augment JULES ensemble design"
author: "Doug McNeall"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The purpose of this vignette is to augment an ensemble of JULES with new ensemble members, with input parameter configurations where we think the model output will fall within a set of constraints. The code will write a new set of configuration files.

```{r packages}

library(julesR)
library(emtools)
library(imptools)
library(viztools)


```



```{r}
 years = 1861:2014
 ysec = 60*60*24*365
 norm_vec = c(1e12, 1e12, 1e12/ysec , 1e12, 1e12, 1e9)
 
 # Load up the data
 lhs_i = read.table('data/ES_PPE_i/lhs_u-ao732.txt', header = TRUE)
 lhs_ii = read.table('data/ES_PPE_ii/lhs_u-ao732a.txt', header = TRUE)
# 
# toplevel.ix = 1:499
# 
# lhs = rbind(lhs_i, lhs_ii)[toplevel.ix, ]
# 
# X = normalize(lhs)
# colnames(X) = colnames(lhs)
# d = ncol(X)


```


```{r, include=FALSE}

# --------------------------------------------------------------------------------
# Level 0 constraint
# Model runs and has some kind of carbon cycle
# --------------------------------------------------------------------------------

# Constrain with global runoff and nbp, so that the emulator
# is not negatively affected by really bad points
# level0.ix = which(dat.norm[,'runoff'] >0.5 & dat.norm[,'nbp'] > -10)
# 
# dat.level0  = dat.norm[level0.ix, ]     # (scaled to sensible) data that passes level 0
# X.level0 = X[level0.ix, ]               # Normalised inputs that pass level 0
# lhs.level0 = lhs[level0.ix, ]           # Non-normalised inputs that pass level 0
# 
# nlevel0.ix = setdiff(allix, level0.ix)  # These inputs DO NOT PASS
# X.nlevel0 = X[nlevel0.ix, ]
# lhs.nlevel0 = lhs[nlevel0.ix, ]
# 
# # These are the ensemble members which do not run (produce NA)
# na.ix = which(is.na(dat.norm[,'runoff']))
# X.na = X[na.ix, ]
# lhs.na = lhs[na.ix, ]


```





Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
