---
title: "Write a JULES ensemble design"
author: "Doug McNeall"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Write a JULES ensemble design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows the creation of a perturbed parameter ensemble design for JULES. It uses a maximin latin hypercube design to create a design of factors, which multiply the standard parameters for JULES. Individual PFTS are all multiplied by the same factor.

On running the code, a folder is created for the configuration file, the latin hypercube, the standard parameters, and allpft standard parameters (these will just be 1s at the moment.)


```{r}
library(julesR)
# Load a list of parameter perturbations
source('default_jules_parameter_perturbations.R')

# Easiest way to generate a design of the right size is to have a "fac" which takes
# the names from the parameter list, and then multiplies everything by 0.5 or 2

tf <- 'l_vg_soil'
# we don't want anything that is TRUE/FALSE to be in fac
fac.init <- names(paramlist)
not_tf.ix <- which(names(paramlist)!=tf)
paramlist.trunc <-paramlist[not_tf.ix]

fac <- names(paramlist.trunc)

maxfac = lapply(paramlist.trunc,function(x) x$max[which.max(x$max)] / x$standard[which.max(x$max)])
minfac = lapply(paramlist.trunc,function(x) x$min[which.max(x$max)] / x$standard[which.max(x$max)])

dir.create('conf_files_example')

write_jules_design(paramlist, n = 100,
                    fac = fac, minfac = minfac, maxfac = maxfac,
                    tf = tf,
                    fnprefix = 'conf_files_example/param-perturb-P',
                    lhsfn = 'conf_files_example/lhs_example.txt',
                    stanfn = 'conf_files_example/stanparms_example.txt',
                    allstanfn = 'conf_files_example/allstanparms_example.txt',
                    rn = 12,
                    startnum = 0)

print(cbind(minfac, maxfac))


# Checking section
lapply(paramlist, function(x) length(x$standard))
lapply(paramlist, function(x) length(x$standard)==length(x$min) & length(x$standard)==length(x$max))

```



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
